---
title: "SOI Measurements"
author: "All"
format: html
execute:
  echo: false
  warning: false
editor: visual
---

```{r}
library(stringr)
library(gridExtra)
library(maptools)
library(ggplot2)
library(ggalt)
library(ggthemes)
library(tibble)
library(viridis)
library(knitr)
library(plotly)
library(egg)
library(ggpubr)
library(GillespieSSA)
library(MASS)
library(rgl)
library(zoo)
library(Sim.DiffProc)
library(doParallel)
library(ggsci)
library(deSolve)
library(pracma)
library(diffeqr)
library(parallel)
library(tidymodels)
library(data.table)
library(glue)

# source("G:\\Other computers\\Il mio laptop\\Francesco\\Università\\Articoli\\Marta\\GSM2\\Dose Rate\\Code\\utilities_doserate.R")

theme_set(theme_bw()+theme(plot.title = element_text(size=20, color="black"),
                           axis.title.x = element_text(size=20, color="black"),
                           axis.title.y = element_text(size=20, color="black"),
                           axis.text.x = element_text(size=20, color="black"),
                           axis.text.y = element_text(size=20, color="black"),
                           legend.title = element_blank(),
                           legend.text = element_text(size=20, color="black")))

cb_a <- c("#0072B2","#000000","#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cb_b <- c("#000000", "#E69F00", "#0072B2", "#6A3D9A" , "#009E73", "#F0E442", "#56B4E9", "#D55E00", "#CC79A7")
cb_c <- c( "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")

cb_nob <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)
```

```{r}
compute_calibration_adc <- function(m, df_count, bin){

  y <- m*c(1:nrow(df_count))
  
  df_y<-data.frame(y = y, counts = df_count$count)
  
  count_h<-c()
  y_h<-c()
  for (b in 1:(length(bin)-1)) {
    count_h[b] <- sum(df_y$counts[(df_y$y > bin[b]) & (df_y$y <= bin[b+1])])
    y_h[b]<-(bin[b]+bin[b+1])/2
  }
  
  fy_h <- data.frame(y = y_h, fy = count_h)
  
  return(fy_h)
}

compute_spectra <- function(fy_h, bin){
  
  hist <- fy_h %>% 
    mutate(BinWidth = diff(bin))
  
  hist$fy_bw <- hist$fy/hist$BinWidth
  
  B <- 1/diff(log10(hist$BinWidth))[1]
  
  # B<-1/0.05
  C <- log(10)*diff(log10(hist$BinWidth))[1]
  
  hist$fy_bw_norm <- hist$fy_bw/(C*sum(hist$y*hist$fy_bw))
  # hist$fy_norm <- (hist$counts)/(C*sum(hist$y*hist$count))
  
  hist$yfy <- hist$fy_bw_norm*hist$y
  
  hist$yfy_norm <- hist$yfy/(C*sum(hist$y*hist$yfy))
  
  hist$ydy <- hist$yfy_norm*hist$y
  
  hist_M <- fy_h %>% 
    mutate(BinWidth = diff(bin))
  
  hist_M$fy_bw<-hist_M$fy/hist_M$BinWidth
  hist_M$fy_bw_norm<-hist_M$fy_bw/(C*sum(hist_M$y*hist_M$fy))
  
  hist_M$yfy<-hist_M$fy_bw*hist_M$y
  hist_M$yfy_norm<-hist_M$yfy/(C*sum(hist_M$y*hist_M$yfy))
  hist_M$ydy<-hist_M$fy_bw*hist_M$y*hist_M$y
  
  #yF value
  yF<-sum(hist_M$BinWidth*hist_M$yfy)/sum(hist_M$BinWidth*hist_M$fy_bw)
  
  #yD value
  yD<-sum(hist_M$BinWidth*hist_M$ydy)/sum(hist_M$BinWidth*hist_M$yfy)
  
  y0<-(150)^2
  
  ystar<-(y0*sum(((1-exp(-(hist$y^2)/(y0)))*hist$BinWidth*hist$fy_bw)))/(yF*sum(hist$BinWidth*hist$fy_bw))
  
  return(list(histogram = hist, yF = yF, yD = yD, ystar = ystar))
}

select_gain <- function(gain){
  if(gain == "M"){
    m <- 0.46
  }else if(gain == "L"){
    m <- 0.444
  }else{
    return(-1)
  }
  
  return(m)
}

```

```{r}
bin<-10^(seq(log10(1),log10(10000),length.out=100))
```

```{r}
cut <- 30
```

## 03/16 - 70 MeV

We made a first measurements at 15 nA but we weren't sure about the gain. This is the results.

```{r}

df <- fread("16March2024\\70MeV_muscle_15nA_.Spe")
count <- as.numeric(df$`$SPEC_ID:`[12:4107]) %>% 
  as.data.frame()
count <- count %>% 
  mutate(channel = 1:nrow(count))
colnames(count)[1] <- "count"
count$count2 <- count$count*count$channel^2
count$Type <- "15nA - muscle"

count$count[which(count$channel < cut)] <- 0

sum(as.numeric(df$`$SPEC_ID:`[12:4107]))/as.numeric(strsplit(df$`$SPEC_ID:`[9]," ")[[1]][1]) 
sum(as.numeric(df$`$SPEC_ID:`[(12 + 21):4107]))/as.numeric(strsplit(df$`$SPEC_ID:`[9]," ")[[1]][2]) 

p <- count %>% 
  filter(channel > cut) %>% 
  ggplot(aes(channel, count2, color = Type)) +
  geom_step(linewidth = 1) +
  scale_x_log10() +
  scale_color_manual(values = cb_b) +
  # geom_vline(xintercept = 570, color = "maroon", linewidth = 1) +
  xlab("Channel") + 
  ylab("Counts")
ggplotly(p)
```

This is the spectra in y.

```{r}
m <- select_gain("M")

fy_h <- compute_calibration_adc(m, count, bin)

df_plot <- data.frame(y = fy_h$y, fy = fy_h$fy)

p_adc <- df_plot %>% 
  ggplot(aes(x=y,y=fy)) +
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra <- compute_spectra(fy_h, bin)
  
p_spec <- spectra$histogram %>% 
  ggplot(aes(y,ydy)) + 
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  ylab("yd(y)")
ggplotly(p_spec)

```

We made other changes that we do not understood, 20 minute measurements with 15nA at 70 MeV protons after muscle.

```{r}
df <- fread("16March2024\\70MeV_muscle_15nA_medium_1.Spe")
count <- as.numeric(df$`$SPEC_ID:`[12:4107]) %>% 
  as.data.frame()
count <- count %>% 
  mutate(channel = 1:nrow(count))
colnames(count)[1] <- "count"
count$count2 <- count$count*count$channel^2
count$Type <- "15nA - muscle"

count$count[which(count$channel < cut)] <- 0

p <- count %>% 
  filter(channel > cut) %>% 
  ggplot(aes(channel, count2, color = Type)) +
  geom_step(linewidth = 1) +
  scale_x_log10() +
  scale_color_manual(values = cb_b) +
  # geom_vline(xintercept = 570, color = "maroon", linewidth = 1) +
  xlab("Channel") + 
  ylab("Counts")
ggplotly(p)

```

```{r}

par <- format(sum(as.numeric(df$`$SPEC_ID:`[(12 + cut):(4107)])),big.mark=",",scientific=FALSE)
par_s <- format(sum(as.numeric(df$`$SPEC_ID:`[(12 + cut):(4107)]))/as.numeric(strsplit(df$`$SPEC_ID:`[9]," ")[[1]][1]),big.mark=",",scientific=FALSE)

glue("Total events: {par}")
glue("Event per second: {par_s}")

```

The spectra in y

```{r}
m <- select_gain("M")

fy_h <- compute_calibration_adc(m, count, bin)

df_plot <- data.frame(y = fy_h$y, fy = fy_h$fy)

p_adc <- df_plot %>% 
  ggplot(aes(x=y,y=fy)) +
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra <- compute_spectra(fy_h, bin)
  
p_spec <- spectra$histogram %>% 
  ggplot(aes(y,ydy)) + 
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```

These are the second and third 20 minute shifts.

```{r}

df_1 <- fread("16March2024\\70MeV_muscle_15nA_medium_2.Spe")
count_1 <- as.numeric(df_1$`$SPEC_ID:`[12:4107]) %>% 
  as.data.frame()
count_1 <- count_1 %>% 
  mutate(channel = 1:nrow(count_1))
colnames(count_1)[1] <- "count"
count_1$count2 <- count_1$count*count_1$channel^2
count_1$Type <- "15nA - muscle - 2"

count_1$count[which(count_1$channel < cut)] <- 0

p <- count %>% 
  filter(channel > cut) %>% 
  ggplot(aes(channel, count2, color = Type)) +
  geom_step(linewidth = 1) +
  scale_x_log10() +
  scale_color_manual(values = cb_b) +
  # geom_vline(xintercept = 570, color = "maroon", linewidth = 1) +
  xlab("Channel") + 
  ylab("Counts")
ggplotly(p)

```

```{r}
df_2 <- fread("16March2024\\70MeV_muscle_15nA_medium_3.Spe")
count_2 <- as.numeric(df_2$`$SPEC_ID:`[12:4107]) %>% 
  as.data.frame()
count_2 <- count_2 %>% 
  mutate(channel = 1:nrow(count_2))
colnames(count_2)[1] <- "count"
count_2$count2 <- count_2$count*count_2$channel^2
count_2$Type <- "15nA - muscle - 3"

count_2$count[which(count_2$channel < cut)] <- 0

p <- count %>% 
  filter(channel > cut) %>% 
  ggplot(aes(channel, count2, color = Type)) +
  geom_step(linewidth = 1) +
  scale_x_log10() +
  scale_color_manual(values = cb_b) +
  # geom_vline(xintercept = 570, color = "maroon", linewidth = 1) +
  xlab("Channel") + 
  ylab("Counts")
ggplotly(p)
```

```{r}
p <- count %>% 
  rbind(count_1, count_2) %>% 
  filter(channel > cut) %>% 
  ggplot(aes(channel, count2, color = Type)) +
  geom_step(linewidth = 1) +
  scale_x_log10() +
  scale_color_manual(values = cb_b) +
  # geom_vline(xintercept = 570, color = "maroon", linewidth = 1) +
  xlab("Channel") + 
  ylab("Counts")
ggplotly(p)
```

```{r}
par <- format(sum(as.numeric(df_2$`$SPEC_ID:`[(12 + cut):(4107)])),big.mark=",",scientific=FALSE)
par_s <- format(sum(as.numeric(df_2$`$SPEC_ID:`[(12 + cut):(4107)]))/as.numeric(strsplit(df_2$`$SPEC_ID:`[9]," ")[[1]][1]),big.mark=",",scientific=FALSE)

glue("Total events: {par}")
glue("Event per second: {par_s}")
```

```{r}

m <- select_gain("M")

fy_h <- compute_calibration_adc(m, count_1, bin)

df_plot_1 <- data.frame(y = fy_h$y, fy = fy_h$fy)

p_adc <- df_plot_1 %>% 
  ggplot(aes(x=y,y=fy)) +
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra_1 <- compute_spectra(fy_h, bin)

p_spec <- spectra_1$histogram %>% 
  ggplot(aes(y,ydy)) + 
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)

fy_h <- compute_calibration_adc(m, count_2, bin)

df_plot_2 <- data.frame(y = fy_h$y, fy = fy_h$fy)

p_adc <- df_plot_2 %>% 
  ggplot(aes(x=y,y=fy)) +
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra_2 <- compute_spectra(fy_h, bin)
  
p_spec <- spectra_2$histogram %>% 
  ggplot(aes(y,ydy)) + 
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)

```

```{r}

fy_h <- compute_calibration_adc(m, count_1, bin)
df_plot_1 <- data.frame(y = fy_h$y, fy = fy_h$fy, 
                        Type = "15nA - muscle - 2")

fy_h <- compute_calibration_adc(m, count_2, bin)
df_plot_2 <- data.frame(y = fy_h$y, fy = fy_h$fy, 
                        Type = "15nA - muscle - 3")

p_adc <- df_plot %>% 
  mutate(Type = "15nA - muscle - 1") %>% 
  rbind(df_plot_1, df_plot_2) %>% 
  ggplot(aes(x=y, y=fy, color = Type)) +
  geom_step(linewidth = 1) +
  scale_color_manual(values = cb_b) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra_ <- spectra$histogram %>% 
  mutate(Type = "15nA - muscle - 1")

spectra_2_ <- spectra_2$histogram %>% 
  mutate(Type = "15nA - muscle - 3")

spectra_1_ <- spectra_1$histogram %>% 
  mutate(Type = "15nA - muscle - 2")

p_spec <- rbind(spectra_, spectra_1_, spectra_2_) %>% 
  ggplot(aes(y, ydy, color = Type)) + 
  geom_step(linewidth = 1) +
    scale_color_manual(values = cb_b) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```

```{r}

count_all <- count
count_all$count <- count$count + count_1$count + count_2$count

fy_h <- compute_calibration_adc(m, count_all, bin)

df_plot_all <- data.frame(y = fy_h$y, fy = fy_h$fy)

p_adc <- df_plot_all %>% 
  ggplot(aes(x=y,y=fy)) +
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra_all <- compute_spectra(fy_h, bin)
  
p_spec <- spectra_all$histogram %>% 
  ggplot(aes(y,ydy)) + 
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```

```{r}
par <- format(sum(count_all$count[which(count_all$channel > cut)]),big.mark=",",scientific=FALSE)

glue("Total events: {par}")
```

```{r}

spectra_all_ <- spectra_all$histogram
spectra_all_$Type <-  "All"

p_spec <- rbind(spectra_, spectra_1_, spectra_2_, spectra_all_) %>% 
  ggplot(aes(y, ydy, color = Type)) + 
  geom_step(linewidth = 1) +
    scale_color_manual(values = cb_b) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```



Primo wet

```{r}
df_w <- fread("18March2024\\70MeV_0-5RW3_15nA_medium_4.Spe")
count_w <- as.numeric(df_w$`$SPEC_ID:`[12:4107]) %>% 
  as.data.frame()
count_w <- count_w %>% 
  mutate(channel = 1:nrow(count_w))
colnames(count_w)[1] <- "count"
count_w$count2 <- count_w$count*count_w$channel^2
count_w$Type <- "15nA - WET - 1"

count_w$count[which(count_w$channel < cut)] <- 0

p <- count_w %>% 
  filter(channel > cut) %>% 
  ggplot(aes(channel, count2, color = Type)) +
  geom_step(linewidth = 1) +
  scale_x_log10() +
  scale_color_manual(values = cb_b) +
  # geom_vline(xintercept = 570, color = "maroon", linewidth = 1) +
  xlab("Channel") + 
  ylab("Counts")
ggplotly(p)

```

```{r}
par <- format(sum(as.numeric(df_w$`$SPEC_ID:`[(12 + cut):(4107)])),big.mark=",",scientific=FALSE)
par_s <- format(sum(as.numeric(df_w$`$SPEC_ID:`[(12 + cut):(4107)]))/as.numeric(strsplit(df_w$`$SPEC_ID:`[9]," ")[[1]][1]),big.mark=",",scientific=FALSE)

glue("Total events: {par}")
glue("Event per second: {par_s}")
```


```{r}

fy_h <- compute_calibration_adc(m, count_w, bin)

df_plot_w <- data.frame(y = fy_h$y, fy = fy_h$fy)

p_adc <- df_plot_w %>% 
  ggplot(aes(x=y,y=fy)) +
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra_w <- compute_spectra(fy_h, bin)

p_spec <- spectra_w$histogram %>% 
  ggplot(aes(y,ydy)) + 
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```

```{r}
spectra_all_ <- spectra_all$histogram
spectra_all_$Type <-  "All"

spectra_w_ <- spectra_w$histogram %>% 
  mutate(Type = "15nA - WET - 1")

p_spec <- rbind(spectra_, spectra_1_, spectra_2_, spectra_all_, spectra_w_) %>% 
  ggplot(aes(y, ydy, color = Type)) + 
  geom_step(linewidth = 1) +
    scale_color_manual(values = cb_b) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```


Second wet 20 minutes shift

```{r}
df_w2 <- fread("18March2024\\70MeV_0-5RW3_15nA_medium_5.Spe")
count_w2 <- as.numeric(df_w2$`$SPEC_ID:`[12:4107]) %>% 
  as.data.frame()
count_w2 <- count_w2 %>% 
  mutate(channel = 1:nrow(count_w2))
colnames(count_w2)[1] <- "count"
count_w2$count2 <- count_w2$count*count_w2$channel^2
count_w2$Type <- "15nA - WET - 2"

count_w2$count[which(count_w2$channel < cut)] <- 0

p <- count_w2 %>% 
  filter(channel > cut) %>% 
  ggplot(aes(channel, count2, color = Type)) +
  geom_step(linewidth = 1) +
  scale_x_log10() +
  scale_color_manual(values = cb_b) +
  # geom_vline(xintercept = 570, color = "maroon", linewidth = 1) +
  xlab("Channel") + 
  ylab("Counts")
ggplotly(p)
```

```{r}
par <- format(sum(as.numeric(df_w2$`$SPEC_ID:`[(12 + cut):(4107)])),big.mark=",",scientific=FALSE)
par_s <- format(sum(as.numeric(df_w2$`$SPEC_ID:`[(12 + cut):(4107)]))/as.numeric(strsplit(df_w2$`$SPEC_ID:`[9]," ")[[1]][1]),big.mark=",",scientific=FALSE)

glue("Total events: {par}")
glue("Event per second: {par_s}")
```

```{r}

fy_h <- compute_calibration_adc(m, count_w2, bin)

df_plot_w2 <- data.frame(y = fy_h$y, fy = fy_h$fy)

p_adc <- df_plot_w2 %>% 
  ggplot(aes(x=y,y=fy)) +
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra_w2 <- compute_spectra(fy_h, bin)

p_spec <- spectra_w2$histogram %>% 
  ggplot(aes(y,ydy)) + 
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```

```{r}

count_all_w <- count_w
count_all_w$count <- count_w$count + count_w2$count

fy_h <- compute_calibration_adc(m, count_all_w, bin)

df_plot_all_w <- data.frame(y = fy_h$y, fy = fy_h$fy)

p_adc <- df_plot_all_w %>% 
  ggplot(aes(x=y,y=fy)) +
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra_all_w <- compute_spectra(fy_h, bin)
  
p_spec <- spectra_all_w$histogram %>% 
  ggplot(aes(y,ydy)) + 
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```

```{r}
spectra_all_ <- spectra_all$histogram
spectra_all_$Type <-  "All"

spectra_all_w_ <- spectra_all_w$histogram
spectra_all_w_$Type <-  "All wet"

spectra_w_ <- spectra_w$histogram %>% 
  mutate(Type = "15nA - WET - 1")

spectra_w2_ <- spectra_w2$histogram %>% 
  mutate(Type = "15nA - WET - 2")

p_spec <- rbind(spectra_, spectra_1_, spectra_2_, spectra_all_, spectra_w_, spectra_w2_, spectra_all_w_) %>% 
  ggplot(aes(y, ydy, color = Type)) + 
  geom_step(linewidth = 1) +
    scale_color_manual(values = cb_b) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```

We restart again on the 18/03 with the third WET. We realigned everything so we see if it agress with previous measurements.

```{r}
df_w3 <- fread("18March2024\\70MeV_0-5RW3_15nA_medium_3.Spe")
count_w3 <- as.numeric(df_w3$`$SPEC_ID:`[12:4107]) %>% 
  as.data.frame()
count_w3 <- count_w3 %>% 
  mutate(channel = 1:nrow(count_w3))
colnames(count_w3)[1] <- "count"
count_w3$count2 <- count_w3$count*count_w3$channel^2
count_w3$Type <- "15nA - WET - 2"

count_w3$count[which(count_w3$channel < cut)] <- 0

p <- count_w3 %>% 
  filter(channel > cut) %>% 
  ggplot(aes(channel, count2, color = Type)) +
  geom_step(linewidth = 1) +
  scale_x_log10() +
  scale_color_manual(values = cb_b) +
  # geom_vline(xintercept = 570, color = "maroon", linewidth = 1) +
  xlab("Channel") + 
  ylab("Counts")
ggplotly(p)
```


```{r}
par <- format(sum(as.numeric(df_w3$`$SPEC_ID:`[(12 + cut):(4107)])),big.mark=",",scientific=FALSE)
par_s <- format(sum(as.numeric(df_w3$`$SPEC_ID:`[(12 + cut):(4107)]))/as.numeric(strsplit(df_w3$`$SPEC_ID:`[9]," ")[[1]][1]),big.mark=",",scientific=FALSE)

glue("Total events: {par}")
glue("Event per second: {par_s}")
```


```{r}

fy_h <- compute_calibration_adc(m, count_w3, bin)

df_plot_w3 <- data.frame(y = fy_h$y, fy = fy_h$fy)

p_adc <- df_plot_w3 %>% 
  ggplot(aes(x=y,y=fy)) +
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra_w3 <- compute_spectra(fy_h, bin)

p_spec <- spectra_w3$histogram %>% 
  ggplot(aes(y,ydy)) + 
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```


```{r}
count_all_w <- count_w
count_all_w$count <- count_w$count + count_w2$count + count_w3$count

fy_h <- compute_calibration_adc(m, count_all_w, bin)

df_plot_all_w <- data.frame(y = fy_h$y, fy = fy_h$fy)

p_adc <- df_plot_all_w %>% 
  ggplot(aes(x=y,y=fy)) +
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  xlab("y [keV/um]") +
  ylab("f(y)")
ggplotly(p_adc)

spectra_all_w <- compute_spectra(fy_h, bin)
  
p_spec <- spectra_all_w$histogram %>% 
  ggplot(aes(y,ydy)) + 
  geom_step(linewidth = 1) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```

```{r}
ydw <- format(spectra_all_w$yD,big.mark=",",scientific=FALSE)
ydm <- format(spectra_all$yD,big.mark=",",scientific=FALSE)

glue("yD WET: {ydw}")
glue("yD material: {ydm}")
```

```{r}
ydw <- format(spectra_all_w$ystar,big.mark=",",scientific=FALSE)
ydm <- format(spectra_all$ystar,big.mark=",",scientific=FALSE)

glue("ystar WET: {ydw}")
glue("ystar material: {ydm}")
```

```{r}
ydw <- format(spectra_all_w$yF,big.mark=",",scientific=FALSE)
ydm <- format(spectra_all$yF,big.mark=",",scientific=FALSE)

glue("yF WET: {ydw}")
glue("yF material: {ydm}")
```

```{r}
spectra_all_ <- spectra_all$histogram
spectra_all_$Type <-  "All"

spectra_all_w_ <- spectra_all_w$histogram
spectra_all_w_$Type <-  "All wet"

spectra_w_ <- spectra_w$histogram %>% 
  mutate(Type = "15nA - WET - 1")

spectra_w2_ <- spectra_w2$histogram %>% 
  mutate(Type = "15nA - WET - 2")

spectra_w3_ <- spectra_w3$histogram %>% 
  mutate(Type = "15nA - WET - 3")

p_spec <- rbind(spectra_, spectra_1_, spectra_2_, spectra_all_, spectra_w_, spectra_w2_, spectra_w3_, spectra_all_w_) %>% 
  ggplot(aes(y, ydy, color = Type)) + 
  geom_step(linewidth = 1) +
    scale_color_manual(values = cb_b) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```

```{r}
spectra_all_ <- spectra_all$histogram
spectra_all_$Type <-  "Material"

spectra_all_w_ <- spectra_all_w$histogram
spectra_all_w_$Type <-  "WET"

spectra_w_ <- spectra_w$histogram %>% 
  mutate(Type = "15nA - WET - 1")

spectra_w2_ <- spectra_w2$histogram %>% 
  mutate(Type = "15nA - WET - 2")

spectra_w3_ <- spectra_w3$histogram %>% 
  mutate(Type = "15nA - WET - 3")

p_spec <- rbind(spectra_all_, spectra_all_w_) %>% 
  ggplot(aes(y, ydy, color = Type)) + 
  geom_step(linewidth = 1) +
  scale_color_manual(values = cb_b) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
```

```{r}
p_spec <- rbind(spectra_all_, spectra_all_w_) %>% 
  ggplot(aes(y, ydy, color = Type)) + 
  geom_step(linewidth = 1) +
  scale_color_manual(values = cb_b) +
  # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
  #   labels = trans_format("log10", math_format(10^.x))) + 
  scale_x_log10(limits = c(30,2000)) +
  ylim(c(0.009,0.032)) +
  # scale_y_log10() +
  ylab("yd(y)")
ggplotly(p_spec)
# plot_spectra <- rbind(spectra_, spectra_1_, spectra_2_, spectra_all_, spectra_w_, spectra_w2_, spectra_w3_, spectra_all_w_)
# cumd <- c()
# for (i in unique(plot_spectra$Type)) {
#   add <- plot_spectra %>% 
#     filter(Type == i) %>% 
#     dplyr::select(ydy) %>% 
#     pull() %>% 
#     cumsum()
#   cumd <- c(cumd,add)
# }
# 
# pcum <- plot_spectra %>% 
#   mutate(Cumulative = cumd) %>% 
#   ggplot(aes(y, Cumulative, color = Type)) + 
#   geom_step(linewidth = 1) +
#   scale_color_manual(values = cb_b) +
#   # scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
#   #   labels = trans_format("log10", math_format(10^.x))) + 
#   scale_x_log10() +
#   scale_y_log10() +
#   ylab("Cumulative yd(y)")
# ggplotly(pcum) 
```

